Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core

### 2006-08-17 BD_radvel/mn060888mj_rev/kurosawa.tex
started revising after ref's comment.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@781 25464f21-6099-402c-b30a-640f1d40d38b

\documentclass[english,useAMS, usenatbib]{mn2e}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

@@

Before applying the cross-correlation technique to our main targets,
we have applied the technique to the radial velocity standard HD~140538
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed échelle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}18.18\pm0.62\,\kmps$
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainty of RV with respect to the template star. 
To determine the $\sigma_{\mathrm{RRV}}$, we have used the following
procedure: (1)~add random gaussian deviate noise to the object spectra using the
corresponding variance spectra, (2)~compute the cross-correlation
curve using the spectra with added noise and the template, (3)~measure
the RV by locating the peak, (4)~repeat 1--3 for 100 times, and compute the standard
deviation of the 100 RV values. This should provide a good estimate of
uncertainties in RVs cased by the uncertainties in the flux levels.
We also estimated the RV uncertainties using the standard deviations on the
mean of the two independent RV measurements obtained from the two
consecutive spectra taken on the same night (c.f.~\citealt{joergens:2006}).
We found that these estimates agreed well with those obtained from
the Monte Carlo method. The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
two epochs are also given in Table~\ref{tab:summary_results}.

@@

To identify an object with a RV variation with a statistical
significance from our sample, we apply the method described by
\citet{maxted:2005}, which we briefly summarize next, to our data.
There are three steps in this method: 
(1)~compute the $\chi^{2}$ by fitting the two-epoch RV data for each 
object with a constant function (a zero-th order polynomial),
(2)~compute the corresponding $\chi^{2}$ probability ($p$),
(3)~designate the object as a non-constant RV object or a binary
candidate if $p<10^{-3}$ (1~per~cent).  When computing $\chi^{2}$, we
use the uncertainties in the relative RV ($\sigma_{\mathrm{RRV}}$). 
The number of degree of freedom in the fitting procedure is obviously
1.  A similar method was also used in a recent RV survey of VLM stars
by \citet{basri:2006}.

@@

\caption{Histogram of the $\chi^2$ probability ($p$) for fitting the
  observed (relative) RV values with a constant (a horizontal
  line). The constant used in the fit is determined from the weighted mean of
  the two RV measurements for each object.  The objects with
  $p<10^{-3}$ are identified as \emph{non-constant} or \emph{multiple},
  which appear in the right-most bin in the histogram. There
  are four objects which satisfy this condition. The
  expected distribution (dashed) for RV constant objects based on the RV
  uncertainties in the observations (Table~\ref{tab:summary_results})
  and based on the $\chi^{2}$ probability function is also shown for a
  comparison.  The match between the expected distribution and the
  histogram is reasonable, indicating that our uncertainty estimates
  in RV values are also reasonable.  }

>>>>

\documentclass[english,useAMS, usenatbib]{mn2e}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{color}

@@

Before applying the cross-correlation technique to our main targets,
we have applied the technique to the radial velocity standard HD~140538
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed échelle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}19.18\pm0.62\,\kmps$
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainty of RV with respect to the template star. 
To determine the $\sigma_{\mathrm{RRV}}$, we have used the following
procedure: (1)~add random gaussian deviate noise to the object spectra using the
corresponding variance spectra\footnote{\textcolor{red}{Defined by the variance of the
chi-square fit to the signal obtained during optimum extraction.}}, 
(2)~compute the cross-correlation
curve using the spectra with added noise and the template, (3)~measure
the RV by locating the peak, (4)~repeat 1--3 for 100 times, and compute the standard
deviation of the 100 RV values. This should provide a good estimate of
uncertainties in RVs cased by the uncertainties in the flux levels.
We also estimated the RV uncertainties using the standard deviations on the
mean of the two independent RV measurements obtained from the two
consecutive spectra taken on the same night (c.f.~\citealt{joergens:2006}).
We found that these estimates agreed well with those obtained from
the Monte Carlo method. The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
two epochs are also given in Table~\ref{tab:summary_results}.

@@

To identify an object with a RV variation with a statistical
significance from our sample, we apply the method described by
\citet{maxted:2005}, which we briefly summarize next, to our data.
There are three steps in this method: 
(1)~compute the $\chi^{2}$ by fitting the two-epoch RV data for each 
object with a constant function (a zero-th order polynomial),
(2)~compute the corresponding $\chi^{2}$ probability ($p$),
(3)~designate the object as a non-constant RV object or a binary
candidate if $p<10^{-3}$ (\textcolor{red}{0.1~per~cent}).  When computing $\chi^{2}$, we
use the uncertainties in the relative RV ($\sigma_{\mathrm{RRV}}$). 
The number of degree of freedom in the fitting procedure is obviously
1.  A similar method was also used in a recent RV survey of VLM stars
by \citet{basri:2006}.

@@

\caption{Histogram of the $\chi^2$ probability ($p$) for fitting the
  observed (relative) RV values with a constant (a horizontal
  line). The constant used in the fit is determined from the weighted mean of
  the two RV measurements for each object.  The objects with
  $p<10^{-3}$ are identified as \emph{non-constant} or \emph{multiple},
  which appear in the right-most bin in the histogram. There
  are four objects which satisfy this condition. 
  \textcolor{red}{The expected distribution (dashed) for RV constant
  objects is also shown for a comparison.} The distribution is
  normalized with the total number of objects that have $p<10^{-3}$.
  The match between the expected distribution and the
  histogram is reasonable, indicating that our uncertainty estimates
  in RV values are also reasonable.  }
